---
title: "overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6.5
)


# 
# output:
#   md_document:
#     variant: markdown_github
# always_allow_html: true
# 

```

# lookatthis package

This package provides two functions for quick display of specific data types.

## 1. Interactive point map

point_map() creates a leaflet map to view point data. Column with coordinate data is detected automatically.


```{r}
suppressPackageStartupMessages(library(lookatthis))

```

The site numbers can be filtered using the ids argument.

```{r, fig.width=6.5, fig.height=4.2, fig.align='center'}
point_map(soil_data)

```
```{r, fig.width=6.5, fig.height=4.2, fig.align='center'}
point_map(soil_data, ids = c(13300:13600))

```

\


## 2. Plot SEM

The package piecewiseSEM provides a method for Structural Equation Modeling. However, their plotting function is Create a figure from a model output from piecewiseSEM.

```{r, fig.width=5, fig.height=5, fig.align='center'}
library(piecewiseSEM)

data <- decomposition_data

pmod <- psem(
  lm(decomposition ~ CN_ratio_litter + earthworm_abundance + detritivore_abundance, data),
  lm(earthworm_abundance ~ CN_ratio_litter + functional_diversity + LAI_canopy , data),
  lm(detritivore_abundance ~ CN_ratio_litter + functional_diversity + herb_cover + LAI_canopy, data),
  lm(LAI_canopy ~ functional_diversity, data),
  lm(herb_cover ~ LAI_canopy, data)
)

summary(pmod)

```

While the summary provides valuable information, nothing beats a figure to get a quick glimpse of what is happening. Here black and red arrows represent positive and negative relationships respectively, with weighted width with the strength of the effect. Grey dashed line represent non-significant effects.

```{r, fig.width=5, fig.height=5, fig.align='center'}
plot_psem(model = pmod)

```

Another layout is also available.
```{r, fig.width=5, fig.height=5, fig.align='center'}
plot_psem(model = pmod, layout = "neato")

```

If additional tweaking is desired, you can export the DOT code directly.
```{r, fig.width=5, fig.height=5, fig.align='center'}
dot_code <- plot_psem(model = pmod, render = F) %>% generate_dot()
cat(dot_code)

```

